---
title: "Probability and Counting"
author: "May Kyaw"
output:
  html_document:
    number_sections: yes    
    toc: yes
  pdf_document:
    toc: yes
---
In this project we will explore empirical probability using random samples. The two important functions to understand are "sample" and "replicate".
We use the sample function to set up our experiment, and replicate function to repeat it as many times as we want.

# Rolling Die
## Fair Die
Setup the experiment where we roll two fair six sided die independently, and calculate the sum of the numbers that appear for each of them. 
```{r}

```
Use the replicate function to repeat this experiment 10000 times, store the output of the experiment in a variable "sum_die". 
```{r}

```
Use "sum_die" to calculate the empirical probability of getting the sums 2, 3, 4, ..., 12. Compare your answers with the theoretical values (you calculated these in HW2).

```{r}

```

## Unfair Die
Repeat the above experiment in the case when one of the die is biased to land on 2 with probability 0.5 and land with probability 0.1 of the other sides. The other die is fair. 

# Coin Tosses
Recall the coin toss problem from HW2: Suppose Sarah and Ali toss two coins indenpendently $n$ times, what is the probability that both of them have the same number of head

## n=2
Setup the coin toss experiment when $n=2$, and calculate the relevant empirical probability. And match it with your theoretical/calculated probability. 
```{r}

```

## n=3
Setup the experiment and repeat the same process as above. 
```{r}

```

## General Case
Now try writing a function for the general case, and check your answers for values of $n=5, 10, 20$.
```{r}

```

# Data Analysis
Load the iris dataset. 
```{r}

```
Use the boxplot function to show side-by-side boxplots for the variable "Petal.Lenght" across the three different species. 

```{r}

```

Use the boxplot function to show side-by-side boxplots for the variable "Sepal.Width" across the three different species. 
```{r}

```

Note at least two observations that you can make looking at these boxplots. 
